### 2015-01-02 mcmc.tex
moving comment
notes to self

\paragraph{Hamiltonian:}
[HOGG: THIS HAS SOME OTHER NAME; WHAT?]
In many cases of interest, the function $f(\pars)$ can be analytically
differentiated, such that it is possible to quickly execute a gradient
$\dd f/\dd\pars$ evaluation.
Indeed, in the modern world of computing, there are even
auto-differentiation systems that deliver automatically code that
produces the gradient of any function you can write.\note{HOGG cite
  autodiff systems}
There is a class of MCMC methods that make use of gradient information
to effectively inform the proposal distribution and thus speed sampling.
... HOGG more here!

@@

>>>>

\paragraph{Hamiltonian:}
[HOGG, DFM: THIS HAS SOME OTHER NAME; WHAT?]
In many cases of interest, the function $f(\pars)$ can be analytically
differentiated, such that it is possible to quickly execute a gradient
$\dd f/\dd\pars$ evaluation.
Indeed, in the modern world of computing, there are even
auto-differentiation systems that deliver automatically code that
produces the gradient of any function you can write.\note{HOGG cite
  autodiff systems}
There is a class of MCMC methods that make use of gradient information
to effectively inform the proposal distribution and thus speed sampling.

... HOGG more here!

@@

% HOGG:  Is the following a repeat from previously and/or does it mesh with what's earlier?
